%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\cvevent{Translator (English-Binary-Morse)}{}{11/2023 - 12/2023}{Towson University}
\link{https://github.com/zeshanbasaran/Translator_Morse-Binary-English}{Translator (English-Binary-Morse) on Github}
Developed a Java program that translates messages between \\ English, Morse code, and ASCII binary code for my COSC 237 final project.
\begin{itemize}
\item Utilized concepts of subclasses, abstract classes, and polymorphism to practice proper code organization.
\end{itemize}

\divider

\cvevent{Movie Sentiment Analysis}{}{01/2023}{Personal Project}
\link{https://github.com/zeshanbasaran/movieSentimentAnalysis}{Movie Sentiment Analysis on Github}
Created a Python program that uses natural language processing (NLP) and machine learning algorithms from scikit-learn to \\ analyze a user's sentiment regarding a movie.
\begin{itemize}
\item Dataset was a collection of IMDB reviews from Kaggle.
\item It recieved 1000 positive and 1000 negative movie reviews from the dataset for training and testing.
\end{itemize}

\divider

\cvevent{Data Analysis for Sensors}{}{12/2022}{Allen Institute (Seattle, WA)}
\link{https://github.com/zeshanbasaran/SensorDataAnalysis}{Sensor Data Analysis on Github}
Composed a program in Python to organize data collected by the institute.
\begin{itemize}
\item Program was created for a connection at the institute, with extensive comments so the researcher could modify the program as necessary.
\item Organized 4,441 data points collected from glutamate sensors.
\end{itemize}